Data Wrangling

### 2019-09-08 code/analysis.Rmd
big update

---
title: "Analysis - Part 1"
subtitle: "PsyFaKo Open Science Survey"
author: "Johannes Brachem"
date: "Last update: `r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    number_sections: yes
    theme: journal
    toc: yes
    toc_depth: 2
    toc_float: 
      collapsed: false
---

# Header
## Load Packages
```{r packages}
# library(formr)
library(tidyverse)
# library(lubridate)
# library(knitr)
# library(kableExtra)
# library(glue)
# library(skimr)
```

## Session Info
```{r session info}
sessionInfo()
```

@@

```{r import data}
main <- read_csv("data/main.csv") %>% 
  filter(field_of_study_mc == "Psychology" | study_degree_field == "Psychology") %>% 
  filter(emp_experience == "Yes")

df_practices <- read_csv("data/df_practices.csv")%>% 
  filter(field_of_study_mc == "Psychology" | study_degree_field == "Psychology") %>% 
  filter(emp_experience == "Yes")
```

@@

```{r}
n_projects_total <- df_practices %>% 
  distinct(id, n_projects) %>% 
  summarise(n = sum(n_projects, na.rm = TRUE)) %>% 
  pull(n)
```

@@

q01.0 <- df_practices %>% 
  group_by(type_of_practice) %>% 
  summarise(n = sum(rp_applied, na.rm = TRUE)) %>% 
  ungroup() %>% 
  mutate(n_projects = n_projects_total) %>% 
  mutate(practices_per_project = n / n_projects_total)

@@

q01 <- df_practices %>% 
  # number of applied practices (per individual and type of project)
  group_by(id, type_of_practice, n_projects) %>% 
  summarise(applied_practices = sum(rp_applied, na.rm = TRUE)) %>% 
  ungroup() %>% 
  mutate(practices_per_project = applied_practices / n_projects) %>%

  # average over individuals
  group_by(type_of_practice) %>% 
  summarise(m = mean(practices_per_project),
            sd = sd(practices_per_project))

@@

```{r}
q02 <- df_practices %>% 
  group_by(id, type_of_practice, project, project_conducted) %>% 
  summarise(n_practice_appl = sum(rp_applied)) %>% 
  ungroup() %>% 
  group_by(type_of_practice, project) %>% 
  summarise(mean = mean(n_practice_appl, na.rm = TRUE), # mean number of applied practices per project
            sd = sd(n_practice_appl, na.rm = TRUE), # sd for number of applied practices per project
            n_conducted = sum(project_conducted), # number of conducted projects
            n_applied = sum(n_practice_appl, na.rm=TRUE)) # number of practice applications

@@

```{r}
q03 <- df_practices %>% 
  filter(rp_applied) %>% 
  group_by(practice, type_of_practice) %>% 
  summarise(n = n_distinct(id)) %>% 
  mutate(n_vp = nrow(main)) %>% 
  mutate(share = (n / n_vp)*100) %>% 
  arrange(share %>% desc()) %>% 
  identity()

@@

```{r}
n_projects <- df_practices %>% 
  ungroup() %>% 
  distinct(id, project, project_conducted) %>% 
  group_by(project) %>% 
  summarise(n = sum(project_conducted)) %>% 
  mutate(order = c(1, 5, 2, 3, 4)) %>% 
  arrange(order)

df_practices$n_project <- rep(n_projects$n, times = nrow(df_practices) / 5)

q04 <- df_practices %>% 
  ungroup() %>% 
  group_by(practice, type_of_practice, project, n_project) %>% 
  summarise(n = sum(rp_applied, na.rm = TRUE)) %>% 
  mutate(share = (n / n_project)*100) %>% 
  arrange(type_of_practice) %>% 
  identity()

@@

```{r}
prereg_where <- main %>% 
  pull(prereg_where)

@@

(prereg_where_data <- tibble(names_prereg_where, prereg_counts))
```

@@

### Share of practice applications
For each practice, we look at the share of projects in which the respective practice was applied.
```{r}
# 
q05 <- df_practices %>% 
  # filter(project %contains% "thesis.bsc" | project %contains% "thesis.msc") %>% 
  filter(rp_applied) %>% 
  group_by(practice, type_of_practice) %>% 
  summarise(n_applied = n()) %>% 
  mutate(n_projects_total = n_projects_total) %>% 
  mutate(share = (n_applied / n_projects_total)*100) %>% 
  arrange(share %>% desc())

@@

```{r}
nosi_q <- df_practices %>% 
  # number of applied practices (per individual and type of project)
  group_by(id, type_of_practice, n_projects, nosi_at_uni) %>% 
  summarise(applied_practices = sum(rp_applied, na.rm = TRUE)) %>% 
  ungroup() %>% 
  mutate(practices_per_project = applied_practices / n_projects)

@@

>>>>

---
title: "Descriptive Analysis"
subtitle: "PsyFaKo Open Science Survey"
author: "Johannes Brachem"
date: "Last update: `r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    number_sections: yes
    theme: journal
    toc: yes
    toc_depth: 2
    toc_float: 
      collapsed: false
---

# Header
## Load Packages

```{r}
source("code/helpers/helper_functions.R")
```

@@

```{r import data}
wide <- read_csv("data/wide.csv") %>% 
  only_psych() %>% filter(emp_experience == "Yes")

long <- read_csv("data/long.csv") %>% 
  only_psych() %>% filter(emp_experience == "Yes")

wide_all <- read_csv("data/wide.csv") %>% only_psych()
stats <- readRDS("data/stats_software.rds")
```

@@

```{r}
n_projects_total <- long %>% 
  distinct(id, n_projects) %>% 
  summarise(n = sum(n_projects, na.rm = TRUE)) %>% 
  pull(n)
```

@@

q01.0 <- long %>% 
  group_by(type_of_practice) %>% 
  summarise(n = sum(rp_applied, na.rm = TRUE)) %>% 
  ungroup() %>% 
  mutate(n_projects = n_projects) %>% 
  mutate(practices_per_project = n / n_projects)

@@

q01 <- long %>% 
  # number of applied practices (per individual and type of project)
  group_by(id, type_of_practice, n_projects) %>% 
  summarise(applied_practices = sum(rp_applied, na.rm = TRUE)) %>% 
  ungroup() %>% 
  mutate(practices_per_project = applied_practices / n_projects) %>%

  # average over individuals
  group_by(type_of_practice) %>% 
  summarise(m = mean(practices_per_project),
            sd = sd(practices_per_project),
            med = median(practices_per_project),
            minimum = min(practices_per_project),
            maximum = max(practices_per_project))

@@

```{r}
q02 <- long %>% 
  group_by(id, type_of_practice, project, project_conducted) %>% 
  summarise(n_practice_appl = sum(rp_applied)) %>% 
  ungroup() %>% 
  group_by(type_of_practice, project) %>% 
  summarise(mean = mean(n_practice_appl, na.rm = TRUE), # mean number of applied practices per project
            sd = sd(n_practice_appl, na.rm = TRUE), # sd for number of applied practices per project
            n_conducted = sum(project_conducted), # number of conducted projects
            n_applied = sum(n_practice_appl, na.rm=TRUE), # number of practice applications
            med = median(n_practice_appl, na.rm = T),
            minimum = min(n_practice_appl, na.rm = T),
            maximum = max(n_practice_appl, na.rm = T))

@@

```{r}
q03 <- long %>% 
  filter(rp_applied) %>% 
  group_by(practice, type_of_practice) %>% 
  summarise(n = n_distinct(id)) %>% 
  mutate(n_vp = nrow(wide)) %>% 
  mutate(share = (n / n_vp)*100) %>% 
  arrange(share %>% desc()) %>% 
  identity()

@@

```{r}
q04.n_projects <- long %>% 
  ungroup() %>% 
  distinct(id, project, project_conducted) %>% 
  group_by(project) %>% 
  summarise(n = sum(project_conducted)) %>% 
  mutate(order = c(1, 5, 2, 3, 4)) %>% 
  arrange(order) %>% 
  arrange(project)

q04.d <- long %>% arrange(project) %>% 
  mutate(q04.n = rep(q04.n_projects$n, each = nrow(long) / 5))

q04 <- q04.d %>% 
  ungroup() %>% 
  group_by(practice, type_of_practice, project, q04.n) %>% 
  # group_by(practice) %>% 
  summarise(n = sum(rp_applied, na.rm = TRUE)) %>% ungroup() %>% 
  # group_by(practice, type_of_practice, project, q04.n) %>% 
  mutate(share = (n / q04.n)*100) %>% 
  arrange(type_of_practice) %>% 
  identity()

@@

```{r}
prereg_where <- wide %>% 
  pull(prereg_where)

@@

prereg_where_data <- tibble(names_prereg_where, prereg_counts) %>% 
  mutate(share = prereg_counts / nrow(wide))
```

@@

### Share of practice applications
For each practice, we look at the share of projects in which the respective practice was applied.
```{r}
n_proj <- long %>% distinct(id, project, project_conducted) %>% 
  summarise(n = sum(project_conducted)) %>% pull(n)

q05 <- long %>% 
  # filter(project %contains% "thesis.bsc" | project %contains% "thesis.msc") %>% 
  filter(rp_applied) %>% 
  group_by(practice, type_of_practice) %>% 
  summarise(n_applied = n()) %>% 
  mutate(n_projects = n_proj) %>% 
  mutate(share = (n_applied / n_projects)*100) %>% 
  arrange(share %>% desc())

@@

```{r}
nosi_q <- long %>% 
  # number of applied practices (per individual and type of project)
  group_by(id, type_of_practice, n_projects, nosi_at_uni) %>% 
  summarise(applied_practices = sum(rp_applied, na.rm = TRUE)) %>% 
  ungroup() %>% 
  mutate(practices_per_project = applied_practices / n_projects)

@@

# Question Block 3: Teaching Coverage, Attitudes
```{r}
# global
n_participants <- nrow(wide_all)
```

## Specific QRPs in teaching
Which of these research practices have been talked about in a critical way in the course of your studies?
```{r QRPs mentioned critically}
q_qrp_t.spec <- wide_all %>% 
  mutate(id = 1:nrow(.)) %>% 
  select(id, study_stage_mc, semester, specific_qrps_teaching) %>% 
  separate(specific_qrps_teaching, into = paste0("qrp.t", 1:11)) %>% 
  gather(qrp.t1:qrp.t11, key = "answer_number", value = "qrp_id") %>% 
  drop_na(qrp_id) %>% 
  mutate(qrp = dplyr::recode(qrp_id, 
                             "1" = "SR of Variables", 
                             "2" =    "No Sample Planning", 
                             "3" =     "Flexible Sample Size", 
                             "4" =    "SR of Conditions", 
                             "5" =   "Flexible Analysis", 
                             "6" =    "Flexible Exclusion", 
                             "7" =    "SR of Hypotheses", 
                             "8" =   "HARKing", 
                             "9" =    "Rounding p-Values", 
                             "10" =   "None", 
                             "11" =   "Not Sure")) %>% 
  select(-answer_number, -qrp_id)

q_qrp_t.spec_share <- q_qrp_t.spec %>% 
  group_by(qrp) %>% summarise(n = n()) %>% ungroup() %>% 
  mutate(share = n / n_participants * 100) %>% arrange(share %>% desc())
```

## Replication Crisis in any lecture

Did you hear about the replication crisis in a lecture?
```{r RC in any lecture}
rc_teaching_general <- wide_all %>% 
  # summarise semesters into year-chunks, 
  # filter(study_stage_mc != "Other") %>% 
  mutate(semester = ifelse(semester %% 2 == 0, semester - 1, semester)) %>% 
  mutate(semester = ifelse(semester > 10, 11, semester)) %>% 
  mutate(semester = ifelse(is.na(semester), "not applicable", semester)) %>% 
  mutate(semester = factor(semester, levels = c(1, 3, 5, 7, 9, 11, "not applicable"),
                           labels = c("1/2", "3/4", "5/6", 
                                      "7/8", "9/10", ">10", "not applicable"))) %>%

  # select relevant variables and summarise
  select(rc_teaching, semester, study_stage_mc) %>% 
  group_by(rc_teaching, semester, study_stage_mc) %>% 
  summarise(n = n()) %>% 
  ungroup() %>%

  # number of participants per semester and study stage
  group_by(semester, study_stage_mc) %>% 
  mutate(n_semester = sum(n)) %>% 
  ungroup() %>%

  # share with respect to students in the same study stage and semester
  mutate(share = (n / n_semester) * 100)

# print
rc_teaching_general %>% 
  arrange(study_stage_mc) %>%  
  print(n = nrow(.))
```

Replication crisis in lectures by university
```{r}
rc_teaching_unis <- wide_all %>%
  group_by(uni_current) %>% mutate(n_uni = n()) %>% ungroup() %>% 
  group_by(uni_current, rc_teaching) %>% 
  mutate(n = n()) %>% ungroup() %>% 
  mutate(share = n / n_uni) %>% 
  distinct(uni_current, n_uni, rc_teaching, n, share) %>% arrange(uni_current)

rc_teaching_unis %>% 
  mutate(share = (share*100) %>% round(1),
         share = paste0("(", share, " %)")) %>% 
  unite(n, share, col = "n", sep = " ") %>% 
  spread(key = rc_teaching, value = n, fill = "0 (0 %)")

rc_teaching_unis.out <- rc_teaching_unis %>% 
  mutate(rc_teaching = factor(rc_teaching, levels = lab.rc_lectures,
                              labels = c("yes", "no", "not_sure"))) %>% 
  unite(n, share, col = "n_share", sep = "_") %>% 
  spread(key = rc_teaching, value = n_share, fill = "0_0") %>% 
  separate(yes, into = c("yes.n", "yes.share"), sep = "_") %>% 
  separate(no, into = c("no.n", "no.share"), sep = "_") %>% 
  separate(not_sure, into = c("not_sure.n", "not_sure.share"), sep = "_") %>% 
  arrange(desc(yes.share)) %>% 
  filter(n_uni >= 30) %>% 
  mutate_at(vars(matches("share")), as.numeric) %>% 
  mutate_at(vars(matches("share")), cop2)
```

## Replication Crisis in which lectures
In which lectures did you hear about the replication crisis?
```{r RC in which lectures}
q_rc_t.spec <- wide_all %>% 
  mutate(id = 1:nrow(.)) %>% 
  separate(rc_teaching_specific, into = paste0("t", 1:11)) %>% 
  select(id, study_stage_mc, semester, t1:t11) %>% 
  gather(t1:t11, key = "answer_number", value = "lecture_id") %>% 
  drop_na(lecture_id) %>% 
  mutate(lecture = dplyr::recode(lecture_id, 
                                 "1" = "General Psychology",
                                 "2" = "Work, Organizational and Economic Psychology",
                                 "3" = "Biological- / Neuropsychology",
                                 "4" = "Diagnostics",
                                 "5" = "Differential Psychology",
                                 "6" = "Introductory Class",
                                 "7" = "Developmental Psychology",
                                 "8" = "Health Psychology",
                                 "9" = "Clinical Psychology",
                                 "10" = "Media- / Communication Psychology",
                                 "11" = "Methods, Stats, Expra",
                                 "12" = "Pedagogical Psychology",
                                 "13" = "Forensic",
                                 "14" = "Social Psychology",
                                 "15" = "Other")) %>% 
  select(-answer_number, -lecture_id)

q_rc_t.spec.share <- q_rc_t.spec %>% 
  group_by(lecture) %>% summarise(n = n()) %>% ungroup() %>% 
  mutate(share = n / n_participants * 100) %>% arrange(share %>% desc())
```

## Attitudes towards replication crisis and open science

```{r}
# table of answers for the three questions
# 1: "not at all"
# 5: "very much"
wide_all %>% 
  select(interest, importance, felt_information) %>% 
  map(table)
```

# Question Block 4: Other

## Statistical Software

```{r}
# print
stats %>% print(n = nrow(.))
```

## Open Science Initiatives
Do you know of an open science initiative at your university?
```{r}
# light wrangling
nosi_aggregation <- wide_all %>% select(nosi, uni_current, nosi_at_uni) %>% 
  group_by(uni_current, nosi_at_uni, nosi) %>% 
  summarise(n = n()) %>% 
  ungroup() %>% 
  mutate(nosi = factor(nosi, levels = c("No", "Not Sure", "Yes"))) %>% 
  arrange(desc(nosi_at_uni))

# compute shares
nosi_agg2 <- nosi_aggregation %>% 
  group_by(uni_current) %>% 
  mutate(n_answers = sum(n)) %>% 
  filter(nosi == "Yes") %>% 
  mutate(share_yes = (n / n_answers) * 100) %>% 
  select(uni_current, nosi_at_uni, n_answers, share_yes) %>% 
  arrange(desc(share_yes))

# print
nosi_agg2
```

Have you heard of open science events (e.g. workshops or talks) at your university=
```{r}
nosi_events <- wide_all %>% select(nosi_events_mc) %>% 
  group_by(nosi_events_mc) %>% 
  summarise(n = n())

nosi_events
```

## Block 3
```{r}
block3 <- list(qrps_teaching = q_qrp_t.spec,
               qrps_teaching_share = q_qrp_t.spec_share,
               rc_teaching_general = rc_teaching_general,
               rc_teaching_unis = rc_teaching_unis.out,
               rc_teaching_specific = q_rc_t.spec,
               rc_teaching_specific_share = q_rc_t.spec.share,
               nosi_data = nosi_agg2,
               nosi_events = nosi_events
               )

saveRDS(block3, "data/block3_results.rds")
```

### 2019-09-08 code/archive/df_practices.Rmd
big update

### Wrangle aggregated data set
```{r qrp_names and orp_names}
qrp_names <- c("SR of Variables", 
               "No Sample Planning", 
               "Flexible Sample Size", 
               "SR of Conditions", 
               "Flexible Analysis", 
               "Flexible Exclusion", 
               "SR of Hypotheses", 
               "HARKing", 
               "Rounding p-Values")

orp_names <- c("Power Analysis", "Preregistration")
```

Turn data frame into long format and split "practice_project" column into two
```{r df_practices turned into long}
df_practices <- main_practices %>% 
  mutate(id = 1:nrow(.)) %>% # create ID for participants

@@

  # if project was not conducted rp_applied should be NA
  mutate(rp_applied = ifelse(project_conducted, rp_applied, NA)) %>%

  # identify university, where a project was most likely conducted
  # mutate(uni_project = ifelse(study_stage_mc !=
  #                               "Bachelor" &
  #                               (project == "thesis.bsc" |
  #                                  project == "emp.intern" |
  #                                  semester <2) & project != "thesis.msc",
  #                             uni_bachelor, as.character(uni_current))) %>%

  # make factors easier to read
  mutate(practice = factor(practice, labels = c(orp_names, qrp_names))) %>% 
  mutate(type_of_practice = ifelse(practice %in% qrp_names, 
                                   "Questionable", "Open")) %>% 
  # mutate(project = factor(project,
  #                         levels = c("emp.intern",
  #                                    "thesis.bsc",
  #                                    "thesis.msc",
  #                                    "project",
  #                                    "other"),
  #                         labels = c("Expra",
  #                                    "Bachelor's Thesis",
  #                                    "Master's Thesis",
  #                                    "Project",
  #                                    "Other"))) %>%

@@

  # select relevant variables
  select(id, project, project_conducted, practice, type_of_practice, 
         n_type_of_practice, rp_applied, n_projects, n_practice_per_project, n_practice_per_type_of_project, nosi_at_uni, field_of_study_mc, study_degree_field, emp_experience) %>%
  arrange(id) %>% 
  ungroup() %>% 
  identity()
```

>>>>

### Wrangle aggregated data set

Turn data frame into long format and split "practice_project" column into two
```{r df_practices turned into long}
long_df <- main_practices %>% 
  mutate(id = 1:nrow(.)) %>% # create ID for participants

@@

  # if project was not conducted rp_applied should be NA
  mutate(rp_applied = ifelse(project_conducted, rp_applied, NA))

df_practices <- long_df %>%

  # identify university, where a project was most likely conducted
  mutate(uni_project = ifelse(study_stage_mc != "Bachelor" &
                                (project == "thesis.bsc" | project == "emp.intern"),
                              uni_bachelor, as.character(uni_current))) %>%
  mutate(uni_project = ifelse(study_stage_mc != "Bachelor" & uni_current != uni_bachelor &
                                (project == "project" | project == "other"),
                              "_unclear", uni_project)) %>% 
  mutate(uni_project = ifelse(project == "thesis.msc", 
                              uni_current, uni_project)) %>% 
  replace_na(list(uni_project = "_unclear")) %>% 
  mutate(q.practice = str_replace(practice, "qrp0", "")) %>% 
  mutate(practice = factor(practice, labels = c(orp_names, qrp_names))) %>% 
  mutate(practice_taught = ifelse(
    str_detect(as.character(specific_qrps_teaching), q.practice), 
    "yes", "no")) %>% 
  select(-q.practice) %>%

  mutate(type_of_practice = ifelse(practice %in% qrp_names, 
                                   "Questionable", "Open")) %>% 
  # mutate(project = factor(project,
  #                         levels = c("emp.intern",
  #                                    "thesis.bsc",
  #                                    "thesis.msc",
  #                                    "project",
  #                                    "other"),
  #                         labels = c("Expra",
  #                                    "Bachelor's Thesis",
  #                                    "Master's Thesis",
  #                                    "Project",
  #                                    "Other"))) %>%

@@

  # select relevant variables
  select(-c(orp01:qrp09)) %>% 
  # select(id, project, project_conducted, practice, type_of_practice, 
  #        n_type_of_practice, rp_applied, n_projects, n_practice_per_project, n_practice_per_type_of_project, nosi_at_uni, field_of_study_mc, study_degree_field, emp_experience) %>%
  arrange(id) %>% 
  ungroup() %>% 
  identity()
```

### 2019-09-08 code/archive/wrangling.Rmd
big update

```{r}
main_start <- read_csv("data/main_start.csv")

# for the purpose of getting excat participantt numbers per university,
# we used the raw data set
# main_start <- read_csv("data/main_raw.csv")
```

# Wrangle Data
## Apply Exclusion Criteria
### Simple Criteria
Note that in main_start.r, we already excluded two participants whose current university was "Amsterdam", because according to our exclusion criteria we only aimed at students in the german-speakinig countries. This had to be done in main_start.r, because we removed some of the information for data protection reasons.
```{r exclusion_01}
main_step01 <- main_start %>% 
  # remove observations that meet exclusion criteria

  filter(created >= as.Date("2018-11-22")) %>%  # filter out data from testing phase
  filter(created <= as.Date("2019-02-28")) %>%  # filter out data from outside sampling period
  filter(!is.na(session), !is.na(ended)) %>% # unfinished sessions
  filter(data_ok == 1) %>% # participant indicated unserious answers (up to here: 1495 observations)
  filter(is.na(study_degree_year) | study_degree_year < 3) %>% # finished studying previous to 2017 (up to here: 1476 observations)

  # identity() for seamless modification of the code above. This allows
  # the user to comment the last line of the pipe-chain without having to adjust
  # the code by removing the pipe from the end of the previous line
  identity()
```

@@

## Fix participant typos

In this chunk, a named vector is defined that is later used to correct typos in the names of participants' denoted universities. Each element is built as `"pattern" = "replacement"`, where the pattern is a regular expression. 
```{r string_replacement}
string_replacement <- c(
  ".*[rR]eg.*" = "Universität Regensburg", 
  ".*[Kk]öln.*" = "Universität zu Köln",
  ".*SRH.*" = "SRH Heidelberg",
  ".*[Gg]ueri.*" = "Otto-von-Guericke-Universität Magdeburg",
  ".*[Ww]ürz.*" = "Julius-Maximilians-Universität Würzburg",
  ".*[Rr][Ww][Tt][Hh].*" = "RWTH Aachen",
  ".*[Aa]a?chen.*" = "RWTH Aachen",
  ".*LMU.*" = "Ludwig-Maximilians-Universität München",
  ".*[oO]snabrück.*" = "Universität Osnabrück",
  ".*[Gg]roningen.*" = "University of Groningen",
  ".*fresenius.*" = "Hochschule Fresenius Düsseldorf")

# The code below allows for the inspection of the strings that are matched by 
# the patterns specified in the code above.
patterns <- names(string_replacement)
# map(patterns, function(x) str_extract(main$uni_current, x) %>% unique())
str_extract(main_step03$uni_current, patterns[1]) %>% unique()

# The code below now uses the `string_replacement` vector from above to 
# correct typos in the main data frame.
main_step04 <- main_step03 %>% 
  mutate(uni_current = str_replace_all(uni_current, string_replacement),
         uni_bachelor = str_replace_all(uni_bachelor, string_replacement))

# The code below replaces answers like `----` in `uni_current` with `NA`.
str_extract(main_step04$uni_current, ".*--.*") %>% unique()
main_step04$uni_current[grepl(".*--.*", main_step04$uni_current)] <- NA
```

@@

```{r}
# helper object
nosi_unis <- c(
  "Ludwig-Maximilians-Universität München",
  "Universität Koblenz-Landau",
  "Fern-Universität in Hagen",
  "Westfälische Wilhelms-Universität Münster",
  "Georg-August-Universität Göttingen",
  "Universität Wien",
  "Humboldt-Universität Berlin",
  "Universität Leipzig",
  "Philipps-Universität Marburg",
  "Universität zu Köln",
  "Universität Zürich",
  "Goethe-Universität Frankfurt",
  "Technische Universität Dresden"
)
```

```{r factor_definition}
main_step05 <- main_step04 %>% 
  # mutate(uni_current = factor(uni_current)) %>% 
  mutate(study_stage_mc = factor(study_stage_mc, 
                                 labels = c("Bachelor", 
                                            "Master", 
                                            "I don't study (any more)", 
                                            "Other")),

         field_of_study_mc = factor(field_of_study_mc,
                                    labels = c("Psychology", 
                                               "Other")),

         emp_experience = factor(emp_experience,
                                 labels = c("Yes", "No")),

         study_degree = factor(study_degree, levels = 1:5,
                               labels = c("B.Sc.", 
                                          "M.Sc.", 
                                          "Diploma", 
                                          "B.A.", 
                                          "M.A.")),

         study_degree_field = factor(study_degree_field, 
                                     labels = c("Psychology", 
                                                "Other")),

         sex = factor(sex, 
                      labels = c("male", "female", "diverse", "no answer")),

         rc_teaching = factor(rc_teaching, 
                              labels = c("Did hear of RC", 
                                         "Did not hear of RC", 
                                         "I don't know")),

         nosi = factor(nosi, labels = c("Yes", "No", "Not Sure")),

@@

         nosi_events_mc = factor(nosi_events_mc, 
                                 labels = c("Yes", "No", "Not Sure")))
```

@@

Include number of projects done per participant and a dummy variable for each individual project per participant.
```{r}
main_step06 <- main_step05 %>% 
  # n_of_projects
  mutate(n_projects_total = str_count(exp_specific, "[0-9]")) %>% 
  mutate(n_projects_total = ifelse(is.na(n_projects_total), 0, n_projects_total)) %>%

  # project dummies
  mutate(n_emp.intern = str_count(exp_specific, "1"),
         n_project =    str_count(exp_specific, "2"),
         n_thesis.bsc = str_count(exp_specific, "3"),
         n_thesis.msc = str_count(exp_specific, "4"),
         n_other =      str_count(exp_specific, "5"))
```

>>>>

```{r import data}
main_start <- read_csv("data/main_start.csv")

# for the purpose of getting excat participantt numbers per university,
# we used the raw data set
main_start <- read_csv("data/main_raw.csv")
```

# Wrangle Data
## Apply Exclusion Criteria
### Simple Criteria
Note that in main_start.r, we already excluded two participants whose current university was "Amsterdam", because according to our exclusion criteria we only aimed at students in the german-speakinig countries. This had to be done in main_start.r, because we removed some of the information for data protection reasons.
```{r exclusion_01}

```

@@

@@

```{r factor_definition}
main_step05 <- main_step04 %>% 
  # mutate(uni_current = factor(uni_current)) %>% 
  mutate(study_stage_mc = factor(study_stage_mc, 
                                 labels = ),

         field_of_study_mc = factor(field_of_study_mc,
                                    labels = ),

         emp_experience = factor(emp_experience,
                                 labels = ),

         study_degree = factor(study_degree, levels = 1:5,
                               labels = ),

         study_degree_field = factor(study_degree_field, 
                                     labels = ),

         sex = factor(sex, 
                      labels = ),

         rc_teaching = factor(rc_teaching, 
                              labels = ),

         nosi = factor(nosi, labels = ),

@@

         nosi_events_mc = factor(nosi_events_mc, 
                                 labels = ))
```

@@

Include number of projects done per participant and a dummy variable for each individual project per participant.
```{r}
main_step06 <- main_step05 %>% add_n_projects()
```

## QRP coverage in teaching

```{r}
main_step06 %>% select(specific_qrps_teaching)

main_step06 %>% 
  separate(specific_qrps_teaching, into = paste0("qrp.t", 1:11)) %>% 
  gather(qrp.t1:qrp.t11, key = "answer_number", value = "qrp_id") %>% 
  drop_na(qrp_id) %>% 
  transmute(qrp = dplyr::recode(qrp_id, 
                             "1" = "SR of Variables", 
                             "2" = "No Sample Planning", 
                             "3" = "Flexible Sample Size", 
                             "4" = "SR of Conditions", 
                             "5" = "Flexible Analysis", 
                             "6" = "Flexible Exclusion", 
                             "7" = "SR of Hypotheses", 
                             "8" = "HARKing", 
                             "9" = "Rounding p-Values", 
                             "10" = "None", 
                             "11" = "Not Sure")) %>% 
  select(qrp)
```

### 2019-09-08 code/archive/wrangling_tmp.Rmd
big update

## Clean Answers about statistical software
```{r}
# regex and replacement for custom answers
stats_repl2 <- c(
  "[Ss][Pp][Ss][Ss]" = "SPSS",
  "^[Rr].*" = "R",
  "_[Rr]$" = "R",
  "G-Power" = "G*Power",
  "[Ss][Tt][Aa][Tt][Aa]" = "STATA",
  "[Jj]amovi" = "Jamovi",
  "SYSTAT" = "Systat",
  "Amos" = "AMOS"
  )

# find maximum number of given answers to know how many columns need to be created
main %>% pull(software1) %>% str_count(",") %>% max()
main %>% pull(software1) %>% unique()

>>>>

## Clean Answers about statistical software
```{r}
# find maximum number of given answers to know how many columns need to be created
main %>% pull(software1) %>% str_count(",") %>% max()
main %>% pull(software1) %>% unique()
